%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-red}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
% \photo[circle,noedge,left]{./profile.jpg}
\name{Lalit}{Kumar}
\position{Senior Software Engineer{\enskip\cdotp\enskip}Frontend}
% \address{42-8, Bangbae-ro 15-gil, Seocho-gu, Seoul, 00681, Rep. of KOREA}

\mobile{(+91) 97-1261-8438} 
\email{lalitkumar.meena.lk@gmail.com}
\github{lalitmee}
\linkedin{lalitmee}
% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
% \skype{skype-id}
% \reddit{reddit-id}
% \medium{madium-id}
% \googlescholar{googlescholar-id}{name-to-display}
%% \firstname and \lastname will be used
% \googlescholar{googlescholar-id}{}
% \extrainfo{extra informations}

\quote{``Be the change that you want to see in the world."}


%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
  {Recruitment Team}
  {Gemini}
  % {Company Name.\\Street Name\\City, India 560102}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Job Application for Senior Software Engineer}
% How the letter is opened
\letteropening{Dear Hiring Manager,}
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
% \letterenclosure[Attached]{Curriculum Vitae}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with the above personal information
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[R]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}
  {Lalit Kumar~~~·~~~Cover Letter}
  {}

% Print the title with the above letter information
\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}

\lettersection{About Me}
As a seasoned Senior Software Engineer with a strong background in frontend development, I bring over 5 years of expertise in delivering high-performance solutions using JavaScript Frameworks. My passion for code quality, mentorship, and continuous learning has been a driving force in my career. I am enthusiastic about tackling challenging tasks and thrive on devising innovative problem-solving methods. What sets me apart is not only my technical proficiency but also my commitment to fostering a collaborative and dynamic team environment. I am excited about the prospect of contributing to Gemini's success and being a part of a company that values innovation, security, and excellence in the cryptocurrency industry.

\lettersection{Why Gemini?}
I am drawn to Gemini because of its reputation as a trailblazer in the cryptocurrency industry, known for its commitment to security, innovation, and user experience. The company's mission to build a more inclusive financial system aligns with my values, and I am eager to contribute my skills as a Senior Software Engineer to support Gemini's vision. The dynamic and collaborative environment at Gemini, coupled with the opportunity to work on cutting-edge technologies, makes it an ideal place for me to leverage my expertise and continue growing in the rapidly evolving fintech landscape.

\lettersection{Why Me?}
As a seasoned Senior Software Engineer with a comprehensive background in frontend development, I bring a unique blend of technical expertise, leadership, and a track record of successfully navigating complex projects. My proficiency in JavaScript Frameworks, coupled with a keen eye for code quality and efficiency, aligns seamlessly with the dynamic and innovative environment at Gemini. What sets me apart is not just my ability to deliver high-performance solutions but also my commitment to mentorship, and fostering a collaborative team culture. I am excited about the opportunity to contribute my skills and experience to elevate the technical landscape at Gemini, and I am confident in my ability to make meaningful contributions to your team's success.

\end{cvletter}


%-------------------------------------------------------------------------------
% Print the signature and enclosures with the above letter information
\makeletterclosing

\end{document}
