\cvsection{Experience}
\begin{cventries}
  \cventry
    {Sr. Software Engineer}
    {KoineArth}
    {Bangalore}
    {April 2021 - Present}
    {
      \begin{cvitems}
        \item{Front-End Lead for \href{https://marketsn.com/}{marketsN} and \href{https://ngagen.com/}{ngageN}.}
        \item{Led a team of 5+ Front-End Developers to develop scalable and highly performant applications.}
        \item{Made a great impact in several areas like code quality, the review process for the code, and user experience by improving the Pull Request Review Process and enforcing some guidelines for code contribution.}
      \end{cvitems}
    }
  \cventry
    {Front End Engineer}
    {Koinearth}
    {Bangalore}
    {August 2019 - March 2021}
    {
        \begin{cvitems}
            \item{Contributed to the development of B2B blockchain baised product(\href{https://marketsn.com/}{marketsN}).}
            \item{We were a team of only two developers handling the whole product from the Front-End side.}
            \item{Wrote a good amount of reusable and highly performant code and delivered it before the deadlines every time.}
            \item{We also got a couple of potential clients for our product which was a great success for us.}
        \end{cvitems}
  }
  \cventry
    {Software Engineer}
    {CognitiveClouds}
    {Bangalore}
    {Jun. 2018 - July 2019}
    {
      \begin{cvitems}
        \item{Worked on real-time projects using technologies like Angular and React.js}
        \item{Learned how to collaborate efficiently in a team of motivated and dedicated developers/engineers.}
      \end{cvitems}
    }
  \cventry
    {Front End Developer (Intern)}
    {The Sense Infinity}
    {Bangalore}
    {Jan. 2018 - May. 2018}
    {
      \begin{cvitems}
        \item{ Implemented a simple desktop application using Electron platform using React.js and Semantic-UI-React.}
        \item {Implemented email templates for the products Ballyhoo and Staple of the Project Sense Infinity}
        \item {Implemented a e-food commerce website using React.js(Javascript) and Laravel(PHP).}
        \item {Implemented Search Engine Optimization(SEO) for the Ballyhoo Web application.}
        \item {API integration by handling the data with the help of React and Redux}
        \item {Improved functionality and performance of the website and worked on Electron Desktop Application Platform.}
      \end{cvitems}
    }
%   \cventry
%     {Web Developer (Intern)}
%     {The Inforwarehouse}
%     {Ahmedabad, Gujarat}
%     {May. 2017 - Jul. 2017}
%     {
%       \begin{cvitems}
%         \item {During this internship, I contributed to their live projects like SkillGames, Ahtaj, etc. These projects were mostly about E-learning Web applications. It was a great experience and I learned a lot from this internship.}
%         \item {\textbf{SkillGames}: This project is based on the concept of Learning by playing games. In this project, you can create your profile and after that, you will be assigned the daily tasks you have to complete daily to improve your learning on the particular topic. Mainly this project is designed for the students to improve their learning criteria. My contribution to this was designing the front end of the dashboard for the user.}
%         \item {\textbf{Ahtaj}: This project was to reduce the effort in consulting with Advocates and Doctors. In this project, you can get an appointment, advice, etc from an Advocate or a Doctor. I was promoted to this project because of my good work in SkillGames. I contributed mainly to the feedback part of the project. The client was giving feedback to correct some mistakes on the website. So I was correcting those mistakes.}
%       \end{cvitems}
%     }

%   \cventry
%     {Volunteer for The Society}
%     {Rural Internship at Atma Vani Welfare Society}
%     {Kanpur, Uttar Pradesh}
%     {Dec. 2016}
%     {
%       \begin{cvitems}
%         \item {This Internship gave me an opportunity to know the rural and slum areas from a different perspective.}
%         \item{During this internship, we visited different schools, an old-age home, and an organization that is working for the deprived section of society.}
%         \item {We also observed the requirement of the IT sector for these welfare organizations for spreading their visions and seeking help for the same.}
%       \end{cvitems}
%     }

\end{cventries}
