%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Development Engineer 2}
    {Quartic.ai}
    {Remote}
    {Apr 2023 - Dec 2023}
    {
      \begin{cvitems}
        \item {Developed end-to-end features on the Quartic Platform using \textbf{React.js}, \textbf{Redux}, \textbf{GraphQL}, and \textbf{Patternfly}.}
        \item {Successfully integrated the \textbf{LDAP Server} with the \textbf{Administration} module, ensuring seamless functionality and providing comprehensive documentation and test cases.}
        \item {Engineered an efficient \textbf{Infinite Virtualized Table} component featuring \textbf{sorting} and shift-select capabilities for streamlined management of \textbf{LDAP Server Users}.}
        \item {Developed rigorous unit and integration \textbf{test cases} to ensure the robustness of each implemented feature.}
        \item {Authored detailed \textbf{documentation} for all new features and changes introduced to the Quartic Platform, enhancing team knowledge and user support.}
        \item {Revamped the \textbf{Analytics(Highcharts)} module using advanced technologies such as \textbf{React Hooks}, \textbf{Context API}, and \textbf{GraphQL} for more efficient data querying and improved user experience.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Software Engineer}
    {KoineArth}
    {Bangalore}
    {Apr 2021 - Mar 2023}
    {
      \begin{cvitems}
        \item{Championed the implementation of a global search feature in \href{https://ngagen.com/}{ngageN}, enhancing the search functionality for NFTs, Creators, and more.}
        \item{Drove the development of high-performance web applications using \textbf{React.js} and \textbf{Next.js}, prioritizing an exceptional user experience.}
        \item{Served as the Front-End Lead for marketsN (B2B blockchain-based supply chain product) and \href{https://ngagen.com/}{ngageN} (NFT marketplace).}
        \item{Led a dynamic team of front-end developers, fostering collaboration and delivering scalable, highly performant applications.}
        \item{Revitalized the \textbf{code review} process by implementing a detailed and self-explanatory Pull Request Template, ensuring a streamlined and effective review process.}
        \item{Significantly contributed to \textbf{code optimization} and \textbf{re-usability} by strictly adhering to \href{https://github.com/airbnb/javascript}{Airbnb-JavaScript} best practices during code reviews.}
        \item{\textbf{Mentored} junior developers, progressively assigning coding tasks to elevate their skills and deepen their understanding of the project's codebase. This approach led to substantial improvements in their coding proficiency.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Front End Engineer}
    {KoineArth}
    {Bangalore}
    {Aug 2019 - Mar 2021}
    {
        \begin{cvitems}
            \item{Contributed to the development of features from scratch for the B2B blockchain-based product marketsN using \textbf{React.js} and \textbf{Next.js}.}
            \item{Contributed to the design of \textbf{Rest APIs} to ensure the desired data structure.}
            \item{Constructed reusable UI components with \textbf{Material-UI}, ensuring cross-browser compatibility.}
            \item{Implemented email templates for orders, invoices, shipments, etc., leveraging \href{https://lit.dev/docs/libraries/standalone-templates/}{lit-HTML} and \href{https://github.com/puppeteer/puppeteer}{puppeteer}.}
            \item{Collaborated closely with the UX/UI design team to deliver pixel-perfect designs, maintaining a strong focus on visual precision.}
        \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer}
    {CognitiveClouds}
    {Bangalore}
    {Jun 2018 - Jul 2019}
    {
      \begin{cvitems}
        \item{Contributed to real-time projects, showcasing proficiency in \textbf{Angular} and \textbf{React.js} technologies.}
        \item{Collaborated effectively within a motivated and dedicated development team, fostering a culture of teamwork.}
        \item{Designed and implemented \textbf{UI components}, addressing \textbf{bugs} and optimizing application performance for enhanced user experience.}
        \item{Initiated and actively participated in knowledge-sharing sessions, promoting continuous learning within the team.}
      \end{cvitems}
    }

%---------------------------------------------------------
  % \cventry
  %   {Front End Developer (Intern)}
  %   {The Sense Infinity}
  %   {Bangalore}
  %   {Jan 2018 - May 2018}
  %   {
  %     \begin{cvitems}
  %       \item{Executed the development of a simple desktop application utilizing the \href{https://www.electronjs.org/}{Electron} platform, crafted with \textbf{React.js} and \href{https://semantic-ui.com/}{Semantic UI}.}
  %       \item{Implemented \textbf{email templates} for invoices in an e-food commerce website.}
  %       \item{Contributed to the development of an e-food commerce website, leveraging the power of \textbf{React.js}.}
  %     \end{cvitems}
  %   }

%---------------------------------------------------------
% \cventry
  %   {Web Developer (Intern)}
  %   {The Inforwarehouse}
  %   {Ahmedabad, Gujarat}
  %   {May. 2017 - Jul. 2017}
  %   {
  %     \begin{cvitems}
  %       \item {During this internship, I contributed to their live projects like SkillGames, Ahtaj, etc. These projects were mostly about E-learning Web applications. It was a great experience and I learned a lot from this internship.}
  %       \item {\textbf{SkillGames}: This project is based on the concept of Learning by playing games. In this project, you can create your profile and after that, you will be assigned the daily tasks you have to complete daily to improve your learning on the particular topic. Mainly this project is designed for the students to improve their learning criteria. My contribution to this was designing the front end of the dashboard for the user.}
  %       \item {\textbf{Ahtaj}: This project was to reduce the effort in consulting with Advocates and Doctors. In this project, you can get an appointment, advice, etc from an Advocate or a Doctor. I was promoted to this project because of my good work in SkillGames. I contributed mainly to the feedback part of the project. The client was giving feedback to correct some mistakes on the website. So I was correcting those mistakes.}
  %     \end{cvitems}
  %   }

  % \cventry
  %   {Volunteer for The Society}
  %   {Rural Internship at Atma Vani Welfare Society}
  %   {Kanpur, Uttar Pradesh}
  %   {Dec. 2016}
  %   {
  %     \begin{cvitems}
  %       \item {This Internship gave me an opportunity to know the rural and slum areas from a different perspective.}
  %       \item{During this internship, we visited different schools, an old-age home, and an organization that is working for the deprived section of society.}
  %       \item {We also observed the requirement of the IT sector for these welfare organizations to spread their visions and seek help for the same.}
  %     \end{cvitems}
  %   }

\end{cventries}