\cvsection{Projects}
\begin{cventries}
  \cventry
    {Developer }
    {Notes-Webapp}
    {React.js, HTML5 and CSS3}
    {Jul. 2017}
    {
      \begin{cvitems}
      \item{\href{https://lalitmee.github.io/Notes-App/}{Link to the Project}: https://lalitmee.github.io/Notes-App/ }
        \item {This is a small project which is developed for taking notes. Mainly it is a web application in which we can take notes as many as we want to. }
        \item{This project was developed mainly to learn basics of React.js and understanding the flow of the mechanism of React.js. It is a very handy web application in which you can edit, add and delete any notes.}
      \end{cvitems}
     }
\end{cventries}
\begin{cventries}
  \cventry
    {Developer }
    {Client Management System}
    {Angular.js, HTML5 and CSS3}
    {Apr. 2017}
    {
      \begin{cvitems}
      \item{\href{https://github.com/lalitmee/Client-Management}{Link to the Project}: https://github.com/lalitmee/Client-Management }
        \item {This is a small project which is developed for management of clients or users in a company or an organization. }
        \item{Management can be done by updating the existing client, deleting the non-existing client and adding the new client.}
      \end{cvitems}
     }
\end{cventries}
\begin{cventries}
  \cventry
    {Developer and Documentation Head}
    {Projectile - Student Project Listing Platform}
    {Django, JavaScript, HTML and CSS}
    {Aug. 2016 - Nov. 2016}
    {
      \begin{cvitems}
      \item{\href{http://projectile.pythonanywhere.com/login/?next=/}{Link to the Project}: http://projectile.pythonanywhere.com/login/?next=/ }
        \item {It is a platform in which we will provide the user with the listing of the suitable projects according to their skills which they currently have. We are trying to reduce the effort and difficulty of the student, interested in doing any project.}
        \item{Anyone who is interested in doing some projects, can go to this website and select according to his skills. Currently, we are working on this website to improve further.}
      \end{cvitems}
     }
\end{cventries}
